Untitled

### 2021-04-29 analysis/chapters/paper_ana_20181122.Rmd
Arreglo figura de RCRV profiles

rad %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  .[sensor %in% c("airs", "iasi") &
      # errinv %between% c(0.0000316227, 1000) & 
      # qc == 0 & 
      # iuse == 1 &
      peakwt %between% c(0.001, 1200)] %>% 
  .[, as.list(quantile(peakwt, c(0.05, 0.5, 0.95))) %>% setNames(c("Q5", "Q50", "Q95")), by = .(sensor, channel)] %>% 
  ggplot(aes(channel, Q50)) +
  # geom_boxplot(aes(group = factor(channel)), outlier.color = "darkorange", 
  #             outlier.size = 0.5, size = 0.1) +
  geom_ribbon(aes(ymin = Q5, ymax = Q95), alpha = 0.4, fill = "darkorange") +
  geom_line(color = "darkorange") +
  scale_y_level(name = "Pressure (hPa)") +
  facet_wrap(~sensor, scales = "free", labeller = labeller(sensor = toupper)) +
  labs(x = "", y = "") +
  theme_minimal() +

@@

rbind(fread(here("analysis", "data", "derived_data", "rcrv_V_perfil.csv")), 
      fread(here("analysis", "data", "derived_data", "rcrv_t_perfil.csv"))) %>% 
  obs.type[., on = "type"] %>%   
  .[type != 130] %>%
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  ggplot(aes(error.level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = factor(code), linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, labeller = labeller(var = c("t" = "Temperature",
                                                "v" = "Wind"))) +
  tag_facets() +
  labs(y = NULL,
       linetype = "",
       color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        aspect.ratio = 2/1)

read_csv(here::here("analysis", "data", "derived_data", "rcrv_satwind.csv")) %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>%
  ggplot(aes(nivel.error, value)) +
  geom_hline(yintercept = c(0, 1), color = "darkgrey") +
  geom_line(aes(color = factor(sat_type), linetype = variable)) +
  scale_color_brewer(palette = "Set1") +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, scales = "free_x", labeller = labeller(var = c("u" = "U wind",
                                                                   "v" = "V wind"))) +
  labs(linetype = NULL,
       color = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        aspect.ratio = 2/1)

files <- Sys.glob("/home/paola.corrales/mesoda/analysis/data/derived_data/rcrv_*_perfil.csv")[1:6]

RCRV <- purrr::map(files, function(f) {
  meta <- unglue::unglue(basename(f), "rcrv_{sensor}_perfil.csv")

  fread(f) %>%
    .[, sensor := meta[[1]][["sensor"]]]
}) %>%
  rbindlist()

RCRV %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  setDT() %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  .[, .(value = mean(value, na.rm = TRUE)), by = .(sensor, level, variable)] %>% 
  ggplot(aes(level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = sensor, linetype = variable)) +
  scale_color_discrete(labels = toupper) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  coord_flip() +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  labs(x = NULL, y = NULL,
       color = NULL, linetype = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom", 
        legend.box = "vertical",
        aspect.ratio = 2/1)

@@

ana[bottom_top %between% c(2, 7), .(v_mean = mean(v)), 
    by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert) +
  scale_fill_continuous_divergingx(super = ScaleDiscretised,
                                   palette = "PRGn", mid = 25,
                                   guide = guide_colorsteps(barwidth = 25,
                                                            barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, size = stat(level)),
                proj = norargentina_lambert, color = "black", 
                breaks = c(-10, -5)) +
  scale_size_continuous(breaks = c(-10, -5), range = c(0.8, 0.4),
                        labels = c("-10", "-5")) +
  # geom_text_contour(aes(z = v_mean), size = 3, stroke = 0.05,
  #                   proj = norargentina_lambert, color = "darkorange", 
  #              breaks = c(-10, -5), skip = 0,
  #              label.placement = label_placement_n(1)) +
  # scale_linetype_manual(guide = NULL, values = c(2, 1)) +
  labs(fill = "Precipitable\nwater (Kg/m²)", size = "V (m/s)") +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +

>>>>

rad %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  .[sensor %in% c("airs", "iasi") &
      # errinv %between% c(0.0000316227, 1000) & 
      # qc == 0 & 
      # iuse == 1 &
      peakwt %between% c(0.001, 1200)] %>% 
  .[, as.list(quantile(peakwt, c(0.05, 0.5, 0.95))) %>% setNames(c("Q5", "Q50", "Q95")), by = .(sensor, channel)] %>% 
  ggplot(aes(channel, Q50)) +
  # geom_boxplot(aes(group = factor(channel)), outlier.color = "darkorange", 
  #             outlier.size = 0.5, size = 0.1) +
  geom_ribbon(aes(ymin = Q5, ymax = Q95), alpha = 0.4) +
  geom_line() +
  scale_y_level(name = "Pressure (hPa)") +
  facet_wrap(~sensor, scales = "free", labeller = labeller(sensor = toupper)) +
  labs(x = "", y = "") +
  theme_minimal() +

@@

rbind(fread(here("analysis", "data", "derived_data", "rcrv_V_perfil.csv")), 
      fread(here("analysis", "data", "derived_data", "rcrv_t_perfil.csv"))) %>% 
  obs.type[., on = "type"] %>%   
  .[type != 130] %>%
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  ggplot(aes(error.level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(linetype = variable, color = code)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_color_brewer(palette = "Dark2") +
  guides(linetype = guide_legend(order = 1),
        color = guide_legend(order = 10)) +
  # scale_color_discrete() +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, labeller = labeller(var = c("t" = "Temperature",
                                                "v" = "Wind"))) +
  tag_facets() +
  labs(x = NULL, y = NULL,
      linetype = NULL, color = "Upper air\nobservations") +
  theme_minimal() +
  theme(legend.box = "vertical",
    aspect.ratio = 4/1) +

  read_csv(here::here("analysis", "data", "derived_data", "rcrv_satwind.csv")) %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>%
  ggplot(aes(error.level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = sat_type, linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_color_brewer(palette = "Set1") +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  coord_flip() +
  facet_wrap(~ var, scales = "free_x", labeller = labeller(var = c("u" = "U wind",
                                                                   "v" = "Wind"))) +
  tag_facets(tag_pool = c("c")) +
  labs(x = NULL, y = NULL,
      linetype = NULL, color = "Satellite-derived\nwind") +
  theme_minimal() +
  theme(legend.box = "vertical",
    aspect.ratio = 2/1) +

  purrr::map(Sys.glob("/home/paola.corrales/mesoda/analysis/data/derived_data/rcrv_*_perfil.csv")[1:6], function(f) {
    meta <- unglue::unglue(basename(f), "rcrv_{sensor}_perfil.csv")
        fread(f) %>%
      .[, sensor := meta[[1]][["sensor"]]]
  }) %>%
  rbindlist() %>% 
  separate(sensor, into = c("sensor", "plat"), sep = "_") %>% 
  setDT() %>% 
  melt(measure.vars = c("mean.y", "sd.y")) %>% 
  .[, .(value = mean(value, na.rm = TRUE),
        var = "Brightness\ntemperature"), by = .(sensor, level, variable)] %>% 
  ggplot(aes(level, value)) +
  geom_hline(yintercept = c(0, 1), color = "grey20") +
  geom_line(aes(color = sensor, linetype = variable)) +
  scale_linetype_manual(values = c("dashed", "solid"),
                        labels = c("Mean RCRV", "SD RCRV")) +
  scale_color_discrete(labels = toupper) +
  coord_flip() +
  scale_x_level(breaks = c(1000, 500, 250, 125, 50)) +
  facet_wrap(~ var, scales = "free_x") +
  tag_facets(tag_pool = c("d")) +
  labs(x = NULL, y = NULL,
      linetype = NULL, color = "Radiances\nobservations") +
  theme_minimal() +
  theme(#legend.position = "bottom", 
    legend.box = "vertical",
    aspect.ratio = 2/1) +

  plot_layout(ncol = 3, widths = c(1, 1, 1), guides = "collect") & theme(legend.box = "vertical")

@@

ana[bottom_top %between% c(2, 7), .(v_mean = mean(v)), 
    by = .(south_north, west_east, date, exp)] %>% 
  .[pw, on = .NATURAL] %>% 
  ggplot(aes(x, y)) +
  geom_contour_fill(aes(z = value, fill = stat(level_d)),
                    proj = norargentina_lambert) +
  colorspace::scale_fill_continuous_divergingx(super = ScaleDiscretised,
                                               palette = "PRGn", mid = 25,
                                               guide = guide_colorsteps(barwidth = 25,
                                                                        barheight = 0.8)) +
  geom_contour2(aes(z = v_mean, size = stat(level)),
                proj = norargentina_lambert, color = "black", 
                breaks = c(-10, -5)) +
  scale_size_continuous(breaks = c(-10, -5), range = c(0.8, 0.4),
                        labels = c("-10", "-5")) +
  # geom_text_contour(aes(z = v_mean), size = 3, stroke = 0.05,
  #                   proj = norargentina_lambert, color = "darkorange", 
  #              breaks = c(-10, -5), skip = 0,
  #              label.placement = label_placement_n(1)) +
  # scale_linetype_manual(guide = NULL, values = c(2, 1)) +
  labs(fill = "Precipitable\nwater (Kg/m²)", size = "V (m/s)") +
  cordillera +
  geom_mapa() +
  facet_grid(. ~ exp, 
             labeller = labeller(exp = c(E2 = "CONV", E5 = "AUT", 
                                         E6 = "SATWND", E8 = "RAD"))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        # legend.box.spacing = margin(0, 0, 0, 0),
        panel.ontop = TRUE,
        panel.grid = element_line(linetype = 3)) +
